### 2018-08-07 paper/security-discussion.tex
Updates security discussion intro

We base our solution on Sphinx~\cite{Sphinx}, which, when used for
onion routing, has been proved to satisfy the properties given
in~\cite{CLOnionRouting} that were shown to result in a UC-secure
onion-routing scheme. We thus primarily need to ensure that
\begin{enumerate*} \item our extension to Sphinxes preserves these
  properties, \item the availability information introduced and
  disseminated to deal with churn satisfies the device-unlinkability
  property we defined in~\cref{system-model}, and that \item the
  resulting node selection does not introduce any advantage for the
  adversary. \end{enumerate*} In terms of general system robustness, a
stateless routing protocol needs to handle packet re-ordering and
network failures (links or nodes).

>>>>

The \ac{SPORES} system is composed of several parts, each of which requires its 
own security analysis.
We thus primarily need to ensure that
\begin{enumerate*}
\item Sphinxes (\cref{Sphinxes}) preserves the properties of 
  \textcite{CLOnionRouting} and \textcite{Sphinx} yielding \ac{UC}-secure 
  \ac{OR};
\item the node selection (\ac{SPOR}, \cref{SPOR}) does not introduce any 
  advantage for the adversary;
\item the availability information introduced and disseminated to deal with 
  churn satisfies the device-unlinkability property we defined in 
  \cref{system-model}; and that
\item the composed protocol (\ac{SPORES}, \cref{SPORES}) provides the desired 
  security properties defined in \cref{system-model}, \ie
  privacy and robustness (packet re-ordering and drops).
\end{enumerate*}
